---
title: "Proba_Candy"
author: "Cédric Hubas"
date: "2024-09-27"
output: 
  github_document:
    toc: true
    toc_depth: 2
  md_document:
    variant: markdown_github
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The following script is a wrapped custom function which calculate the binomial distribution with parameters n and p and plot the discrete probability distribution of the number of successes (xi) in a sequence of n independent experiments, each asking a yes–no question, and each with its own Boolean-valued outcome: success (with probability p) or failure (with probability q = 1-p)

## Details of the experiment
Material:
- A 45g pack of a famous brand of color-varied sugar-coated chocolate dragée.
- a cup

Experiment: Perform a sequence of 5 independent random draws of candies in the 45g pack, with replacement. Answer each time the following yes–no question: is the candy blue ?

Variable X: Number of successes (i.e. nbr of blue sweets) after 5 random draws with replacement (xi={0,1,2,3,4,5})

## Packages

```{r}
library(ggplot2)
```

## Custom function
```{r}
make_my_MMs_plot <- function(n=5,p=0.15) {
  nbrB<-c(0:n)
  Cnx<-factorial(n)/(factorial(nbrB)*(factorial(n-nbrB)))
  probB<-NULL
  for(i in 1:(n+1)) {
    probB[i]<-Cnx[i]*p^nbrB[i]*(1-p)^(n-nbrB[i])
  }
  dataMMs<-data.frame(nbrB=factor(nbrB),
                      prob=probB)
  ggplot(dataMMs,aes(x=nbrB,
                     y=probB))+
    geom_bar(stat = "identity",
             col="#4058F5",
             fill="#4058F5")+
    ylab("Probability")+
    xlab("X (nbr of blue M&M's)")+
    ggtitle(paste("n=",n,"and p=",p))+
    theme_bw(base_size = 14)
}
```

## Plot
```{r}
make_my_MMs_plot() # plot with default values: 5 draws and a probabiliyt of success of 0.15
make_my_MMs_plot(n=20,p=0.4) # plot for 20 draws and a probability of success of 0.4
```
